Report on the Fourth Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE4)

### 2017-05-03 WSSSPE4_report/WSSSPE4_report.tex

This report is based on the events at the workshop and the submitted materials.
There events included discussion of the WSSSPE mission and vision, a keynote,
a set of presentations, a panel, and a number of working groups.  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.

@@

While these points are valid in any type of software, scientific software is even more sensitive to sustainability intents, being in charge of supporting science.

>>>>

This report is based on the events at the workshop and the submitted materials.
These events included discussion of the WSSSPE mission and vision, a keynote,
a set of presentations, a panel, and a number of working groups.  One full day of the
workshop was spent with participants in the working groups, which occurred in parallel
with each other.  And each of the working groups left with a plan for how they could move
forward.

@@
